Non-stationary local time-frequency transform

### 2021-02-26 tf/paper.tex
2021年 2月26日 星期五 16时03分15秒 CST

\inputdir{vecta}
\multiplot{2}{vpp,vss}{width=0.45\textwidth}{Multi-component data registration example. (a) PP image. (b) PS image. }

\multiplot{4}{ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}

\multiplot{3}{before,after,after1}{width=0.48\textwidth}{Interleaved data comparisons. Interleaved data before registration (a), after registration using the traditional LTFT method (b), and after registration using the non-stationary LTFT method (c). \wen{The green boxes highlight an area that shows apparent registration difference in these results. The green boxes are also zoomed for a better view in Figure \ref{fig:before-z,after-z,after1-z}.}}

\multiplot{3}{before-z,after-z,after1-z}{width=0.5\textwidth}{\wen{Zoomed comparison of the green boxes in Figure \ref{fig:before,after,after1}. The coherency of the interleaved PP-PS image has been dramatically enhanced from top to bottom.}}

>>>>

%\inputdir{vecta}
%\multiplot{2}{vpp,vss}{width=0.45\textwidth}{Multi-component data registration example. (a) PP image. (b) PS image. }
%
%\multiplot{4}{ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}
%
%\multiplot{3}{before,after,after1}{width=0.48\textwidth}{Interleaved data comparisons. Interleaved data before registration (a), after registration using the traditional LTFT method (b), and after registration using the non-stationary LTFT method (c). \wen{The green boxes highlight an area that shows apparent registration difference in these results. The green boxes are also zoomed for a better view in Figure \ref{fig:before-z,after-z,after1-z}.}}
%
%\multiplot{3}{before-z,after-z,after1-z}{width=0.5\textwidth}{\wen{Zoomed comparison of the green boxes in Figure \ref{fig:before,after,after1}. The coherency of the interleaved PP-PS image has been dramatically enhanced from top to bottom.}}
%
